---
title: "TellME Europe DGVMTools Benchmarking"
author: "Karl Piltz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true  # Optional: Table of Contents
    toc_depth: 2  # Optional: Adjust TOC depth
    toc_float: true  # Optional: Floating TOC
---
```{r setup, include=FALSE}
library(ggplot2)
theme_set(theme_bw())
library(DGVMBenchmarks)
library(DGVMTools)
library(TellMeEurope)
library(knitr)
library(dplyr)
library(kableExtra)
library(tictoc)
library(ggpubr)
library(yaml)
library(showtext) 
showtext_auto()
# start timer
tic()
```
# Settings {.tabset}

## Hide settings

## Show settings
```{r settings,  echo=F, warning=FALSE}
source(file.path(system.file("TellMeEurope_config.R", package = "DGVMBenchmarks"))) 

str(input, max.level = 2)

# plot maps (turn off to save time)
do_plots <- input[["Switches"]][["do_plots"]]
# switches for which benchmarks to do
do_agpp <- input[["Switches"]][["do_agpp"]]
do_cmass <- input[["Switches"]][["do_cmass"]]
do_stem_density <- input[["Switches"]][["do_stem_density"]]
do_qdbh <- input[["Switches"]][["do_qdbh"]]
do_woody_growth <- input[["Switches"]][["do_woody_growth"]]
do_profound <- input[["Switches"]][["do_profound"]]
do_cmass_pft <- input[["Switches"]][["do_cmass_pft"]]
do_cmass_pft1 <- input[["Switches"]][["do_cmass_pft1"]]
```
***
# AGPP {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["AGPP"]][["Dataset_description"]])
```

## AGPP difference Plots 
```{r Difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_agpp){
  # Define which benchmark to do
benchmark_name <- "AGPP"

# Process your dataset
Data.year.mean <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name, simulation = 1)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, simulation = 1, Data.year.mean, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_simulation_Sources_list[[1]]@name, old_model = all_simulation_Sources_list[[2]]@name)

## Spatial plotting of your comparisons, handels multiple layers to.
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

## Table making, extracts the spatial mean from your fields.
summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets[[1]]) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## AGPP Scatterplots 
```{r AGPP_SCATTER, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_plots && length(all_datasets) > 0){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# Cmass {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["CMASS"]][["Dataset_description"]])
```

## Cmass Difference plots
```{r Cmass, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_cmass){
benchmark_name <- "CMASS"
  
Data.year.mean <- processDataSource(all_datasets, input, benchmark_name,spatial.extent = spatial.extent, simulation = 1, dataset = 1)

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 1, Data.year.mean, spatial.extent)

field_lists <- getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_simulation_Sources_list[[1]]@name, old_model = all_simulation_Sources_list[[2]]@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)

if(length(this_benchmark@datasets[[1]]) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Cmass Scatterplots
```{r cmass scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && length(all_datasets) > 0){plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# Stem Density {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["STEM_DENSITY"]][["Dataset_description"]])
```

## Difference 
```{r Stemdensity, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_stem_density){
benchmark_name <- "STEM_DENSITY"

Data.year.mean <- processDataSource(all_datasets, input, benchmark_name,spatial.extent = spatial.extent, simulation = 1, dataset = 1)

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 1, Data.year.mean, spatial.extent)

field_lists <- getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]
all_sim_full[[2]] <- convertUnits(all_sim_full[[2]],"indiv/m2","indiv/ha")
all_sim_full[[1]] <- convertUnits(all_sim_full[[1]],"indiv/m2","indiv/ha")
all_Fields_list[[2]] <- convertUnits(all_Fields_list[[2]],"indiv/m2","indiv/ha")
all_Fields_list[[3]] <- convertUnits(all_Fields_list[[3]],"indiv/m2","indiv/ha")

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_simulation_Sources_list[[1]]@name, old_model = all_simulation_Sources_list[[2]]@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
if(length(this_benchmark@datasets[[1]]) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Stem Density Scatterplots
```{r Stemdensity scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && length(all_datasets) > 0){plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# QDBH {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["QDBH"]][["Dataset_description"]])
```

## QDBH Difference
```{r QDBH, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_qdbh){
benchmark_name <- "QDBH"

Data.year.mean <- processDataSource(all_datasets, input, benchmark_name,spatial.extent = spatial.extent, simulation = 1, dataset = 1)

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 1, Data.year.mean, spatial.extent)

field_lists <- getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_simulation_Sources_list[[1]]@name, old_model = all_simulation_Sources_list[[2]]@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
if(length(this_benchmark@datasets[[1]]) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## QDBH Scatterplots
```{r QDBH Scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && length(all_datasets) > 0){plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# Woody Growth {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["W_GROWTH"]][["Dataset_description"]])
```

## Woody Growth Difference
```{r Woody growth difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_woody_growth){
benchmark_name <- "W_GROWTH" 

Data.year.mean <- processDataSource(all_datasets, input, benchmark_name,spatial.extent = spatial.extent, simulation = 1, dataset = 1)

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 1, Data.year.mean, spatial.extent)

field_lists <- getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_simulation_Sources_list[[1]]@name, old_model = all_simulation_Sources_list[[2]]@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)

if(length(this_benchmark@datasets[[1]]) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Woody Growth Scatter
```{r Woody growth scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && length(all_datasets) > 0){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# pft cmass difference {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["CMASS_pft"]][["Dataset_description"]])
```

## pft cmass comparison

```{r pft cmass difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide',out.width = "120%",out.height="120%"}
if (do_cmass_pft){
benchmark_name <- "CMASS_pft" 

Data.year.mean <- processDataSource(all_datasets, input, benchmark_name,spatial.extent = spatial.extent, simulation = 1, dataset = 1)

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 1, Data.year.mean, spatial.extent)

field_lists <- getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_simulation_Sources_list[[1]]@name, old_model = all_simulation_Sources_list[[2]]@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}}
```
# pft cmass {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["CMASS_pft"]][["Dataset_description"]])
```

## pft cmass 

```{r pft cmass, echo=FALSE, message=FALSE, warning=FALSE, results='hide',out.width = "120%",out.height="120%"}
if (do_cmass_pft1){
benchmark_name <- "CMASS_pft" 

Data.year.mean <- processDataSource(all_datasets, input, benchmark_name,spatial.extent = spatial.extent, simulation = 1, dataset = 1)

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 1, Data.year.mean, spatial.extent)

field_lists <- getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]



if(do_plots){plotSpatialField(Benchmark = this_benchmark, all_Fields_list = all_Fields_list)}}
```

# Summary table spatial mean
```{r Summary table, echo=FALSE, message=FALSE, warning=FALSE}
 if(nrow(summary_table) > 0) {
   kable(summary_table) %>% kable_styling(full_width = TRUE)}
```

# Model-data Agreement Metrics 
```{r Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(metric_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  metric_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", metric_table$Metric)
  #metric_table$input[["Directory"]][["New_id"]] <- as.numeric(metric_table$input[["Directory"]][["New_id"]])
  #metric_table$input[["Directory"]][["New_id"]] <- sprintf("%.3f", metric_table$input[["Directory"]][["New_id"]])
   #print the table
  kable(metric_table) %>% kable_styling(full_width = TRUE)}
```

# Profound {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["Profound"]][["Dataset_description"]])
```

## LAI
```{r Profound LAI, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_lai"

 this_dataset_run_dir <- file.path(all_datasets[[1]]@dir, input[["Directory"]][["Simulation_name"]][[2]])
 if(file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]], ".out"))) ||  file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]],".out.gz"))))
     this_data_Source <- all_datasets[[1]]
     this_data_Source@dir <- this_dataset_run_dir
 
     Data.year.mean <- DGVMTools::getField(source = this_data_Source, quant = input[[benchmark_name]][["File_name"]])
    Data.year.mean@source@name <- input[[benchmark_name]][["Dataset_name"]] 

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 2, Data.year.mean, spatial.extent)

Profound_table <- TellMeEurope::fullProfoundBenchmark(Benchmark = this_benchmark,all_simulation_Sources_list = all_simulation_Sources_list)}
```

## CMASS
```{r Profound CMASS, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_cmass"
this_dataset_run_dir <- file.path(all_datasets[[1]]@dir, input[["Directory"]][["Simulation_name"]][[2]])
if(file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]], ".out"))) ||  file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]],".out.gz"))))
    this_data_Source <- all_datasets[[1]]
    this_data_Source@dir <- this_dataset_run_dir

    Data.year.mean <- DGVMTools::getField(source = this_data_Source, quant = input[[benchmark_name]][["File_name"]])
    Data.year.mean@source@name <- input[[benchmark_name]][["Dataset_name"]] 

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 2, Data.year.mean, spatial.extent)


Profound_table <- TellMeEurope::fullProfoundBenchmark(Benchmark = this_benchmark,all_simulation_Sources_list = all_simulation_Sources_list)
  
}
```

## DENSITY
```{r Profound DENS, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_dens"
this_dataset_run_dir <- file.path(all_datasets[[1]]@dir, input[["Directory"]][["Simulation_name"]][[2]])
if(file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]], ".out"))) ||  file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]],".out.gz"))))
    this_data_Source <- all_datasets[[1]]
    this_data_Source@dir <- this_dataset_run_dir

    Data.year.mean <- DGVMTools::getField(source = this_data_Source, quant = input[[benchmark_name]][["File_name"]])
    Data.year.mean@source@name <- input[[benchmark_name]][["Dataset_name"]] 

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 2, Data.year.mean, spatial.extent)


Profound_table <- TellMeEurope::fullProfoundBenchmark(Benchmark = this_benchmark,all_simulation_Sources_list = all_simulation_Sources_list)
  
}
```

## QDBH
```{r Profound QDBH, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_diam_g_plus10cm_sts_ext_st_mean"

this_dataset_run_dir <- file.path(all_datasets[[1]]@dir, input[["Directory"]][["Simulation_name"]][[2]])
if(file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]], ".out"))) ||  file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]],".out.gz"))))
    this_data_Source <- all_datasets[[1]]
    this_data_Source@dir <- this_dataset_run_dir

    Data.year.mean <- DGVMTools::getField(source = this_data_Source, quant = input[[benchmark_name]][["File_name"]])
    Data.year.mean@source@name <- input[[benchmark_name]][["Dataset_name"]] 

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 2, Data.year.mean, spatial.extent)


Profound_table <- TellMeEurope::fullProfoundBenchmark(Benchmark = this_benchmark,all_simulation_Sources_list = all_simulation_Sources_list)
  
}
```

## DBH
```{r Profound DBH, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_diam_plus10cm_sts_ext_st_mean"
this_dataset_run_dir <- file.path(all_datasets[[1]]@dir, input[["Directory"]][["Simulation_name"]][[2]])
if(file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]], ".out"))) ||  file.exists(file.path(this_dataset_run_dir, paste0(input[[benchmark_name]][["File_name"]],".out.gz"))))
    this_data_Source <- all_datasets[[1]]
    this_data_Source@dir <- this_dataset_run_dir

    Data.year.mean <- DGVMTools::getField(source = this_data_Source, quant = input[[benchmark_name]][["File_name"]])
    Data.year.mean@source@name <- input[[benchmark_name]][["Dataset_name"]] 

this_benchmark <- createBenchmark(benchmark_name, input, simulation = 2, Data.year.mean, spatial.extent)


Profound_table <- TellMeEurope::fullProfoundBenchmark(Benchmark = this_benchmark,all_simulation_Sources_list = all_simulation_Sources_list)
  
}
```

## Profound metric table
```{r Profound Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(Profound_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  Profound_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", Profound_table$Metric)
  Profound_table$`New Model Run` <- as.numeric(Profound_table$`New Model Run`)
  Profound_table$`New Model Run` <- sprintf("%.3f", Profound_table$`New Model Run`)
  Profound_table$`Old Model Run` <- as.numeric(Profound_table$`Old Model Run`)
  Profound_table$`Old Model Run` <- sprintf("%.3f", Profound_table$`Old Model Run`)
   #print the table
  kable(Profound_table) %>% kable_styling(full_width = TRUE)}
```


# Timing
Total run time:
``` {r time,echo=FALSE,message=FALSE}
# report total run time
toc()
```
