---
title: "TellME Europe DGVMTools Benchmarking"
author: "Karl Piltz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true  # Optional: Table of Contents
    toc_depth: 2  # Optional: Adjust TOC depth
    toc_float: true  # Optional: Floating TOC
---
```{r setup, include=FALSE}
library(ggplot2)
theme_set(theme_bw())
library(DGVMBenchmarks)
library(DGVMTools)
library(TellMeEurope)
library(knitr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(kableExtra)
library(tictoc)
library(ggpubr)
library(yaml)
library(showtext) 
library(data.table)
library(patchwork)
library(extrafont) 
library(ggthemes)
library(ggrepel)
showtext_auto()
# start timer
tic()
```
# Settings {.tabset}

## Hide settings

## Show settings
```{r settings,  echo=F, warning=FALSE}
source(file.path(system.file("TellMeEurope_config.R", package = "DGVMBenchmarks"))) 

#str(input, max.level = 4)

# plot maps (turn off to save time)
do_plots <- as.logical(input[["Switches"]][["do_plots"]])
# Make table for forest fraction
do_forest_fraction <- as.logical(input[["Switches"]][["do_forest_fraction"]])
# switches for which benchmarks to do
do_agpp <- as.logical(input[["Switches"]][["do_agpp"]])
do_cmass <- as.logical(input[["Switches"]][["do_cmass"]])
do_stem_density <- as.logical(input[["Switches"]][["do_stem_density"]])
do_qdbh <- as.logical(input[["Switches"]][["do_qdbh"]])
do_woody_growth <- as.logical(input[["Switches"]][["do_woody_growth"]])
do_profound <- as.logical(input[["Switches"]][["do_profound"]])
do_cmass_pft <- as.logical(input[["Switches"]][["do_cmass_pft"]])
do_cmass_pft1 <- as.logical(input[["Switches"]][["do_cmass_pft1"]])
do_cpool <- as.logical(input[["Switches"]][["do_cpool"]])
do_Regrowth <- as.logical(input[["Switches"]][["do_Regrowth"]])
do_storm <- as.logical(input[["Switches"]][["do_storm"]])
do_SIMFIRE <- as.logical(input[["Switches"]][["do_SIMFIRE"]])
do_BLAZE <- as.logical(input[["Switches"]][["do_BLAZE"]])
do_ICOS_GPP <- as.logical(input[["Switches"]][["do_ICOS_GPP"]])
do_ICOS_NEE <- as.logical(input[["Switches"]][["do_ICOS_NEE"]])
do_ICOS_Reco <- as.logical(input[["Switches"]][["do_ICOS_Reco"]])
do_ICOS_ET <- as.logical(input[["Switches"]][["do_ICOS_ET"]])
do_FLUXNET_GPP <- as.logical(input[["Switches"]][["do_FLUXNET_GPP"]])
do_FLUXNET_NEE <- as.logical(input[["Switches"]][["do_FLUXNET_NEE"]])
do_FLUXNET_Reco <- as.logical(input[["Switches"]][["do_FLUXNET_Reco"]])
```
***
# AGPP {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["AGPP1"]][["Data"]][["Dataset_description"]])
```

## AGPP difference Plots 
```{r Difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_agpp){
  # Define which benchmark to do
benchmark_name <- "AGPP1"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

## Spatial plotting of your comparisons, handels multiple layers to.
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "difference")}

## Table making, extracts the spatial mean from your fields.
summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## AGPP Scatterplots 
```{r AGPP_SCATTER, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_plots && do_agpp){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# Cmass {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["CMASS1"]][["Data"]][["Dataset_description"]])
```

## Cmass Difference plots
```{r Cmass, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_cmass){
benchmark_name <- "CMASS1"
  
Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)

if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}

}
```

## Cmass Scatterplots
```{r cmass scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_cmass){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# Stem Density {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["STEM_DENSITY1"]][["Data"]][["Dataset_description"]])
```

## Difference 
```{r Stemdensity, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_stem_density){
benchmark_name <- "STEM_DENSITY1"

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name,spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]
all_sim_full[[2]] <- convertUnits(all_sim_full[[2]],"indiv/m2","indiv/ha")
all_sim_full[[1]] <- convertUnits(all_sim_full[[1]],"indiv/m2","indiv/ha")
all_Fields_list[[2]] <- convertUnits(all_Fields_list[[2]],"indiv/m2","indiv/ha")
all_Fields_list[[3]] <- convertUnits(all_Fields_list[[3]],"indiv/m2","indiv/ha")

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Stem Density Scatterplots
```{r Stemdensity scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_stem_density){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# QDBH {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["QDBH1"]][["Data"]][["Dataset_description"]])
```

## QDBH Difference
```{r QDBH, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_qdbh){
benchmark_name <- "QDBH1"

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## QDBH Scatterplots
```{r QDBH Scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_qdbh){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# Woody Growth {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["W_GROWTH1"]][["Data"]][["Dataset_description"]])
```

## Woody Growth Difference
```{r Woody growth difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_woody_growth){
benchmark_name <- "W_GROWTH1" 

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)

if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}


}
```

## Woody Growth Scatter
```{r Woody growth scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_woody_growth){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

# PFT CMASS {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["CMASS_pft1"]][["Data"]][["Dataset_description"]])
```

## Difference

```{r pft cmass difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide',out.width = "120%",out.height="120%"}
if (do_cmass_pft){
benchmark_name <- "CMASS_pft1" 

Datasets <- list()

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}
}
```



## Total PFT Cmass

```{r pft cmass, echo=FALSE, message=FALSE, warning=FALSE, results='hide',out.width = "120%",out.height="120%"}
if (do_cmass_pft1){
benchmark_name <- "CMASS_pft1" 

Data.year.mean <- list()

this_benchmark <- createBenchmark(benchmark_name, input, Data.year.mean, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

if(do_plots){plotSpatialField(Benchmark = this_benchmark, all_Fields_list = all_Fields_list)}
}
```
# Regrowth

```{r Regrowth, echo=FALSE, message=FALSE, warning=FALSE, results='hide',out.width = "120%",out.height="120%"}
if (do_Regrowth){
benchmark_name <- "REGROWTH" 

Data.year.mean <- list()

this_benchmark <- createBenchmark(benchmark_name, input, Data.year.mean, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

if(do_plots){Regrowth(this_benchmark,all_sim_full)}
}
```

# Storm {.tabset}

```{r storm desc, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["STORM"]][["Description"]])
```

## Storm Damage 
```{r Storm damage, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_storm){
  # Define which benchmark to do
benchmark_name <- "STORM"

# Process your dataset
Datasets <- list()

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

storm_table<-plotStormScatter(this_benchmark, all_sim_full, do_plots, anno.hjust = 140)

}
```

## Country Table
```{r storm table, echo=FALSE, message=FALSE, warning=FALSE}
if (do_storm){
  storm_table <- storm_table %>%
  mutate(
    Reported_Damage = round(Reported_Damage, 2),
    Modelled_Damage_Before_Calibration = round(Modelled_Damage_Before_Calibration, 2),
    Modelled_Damage_After_Calibration = round(Modelled_Damage_After_Calibration, 2)
  )
  storm_table <- storm_table %>%
  rename(
    Country = `Country`,
    `Reported Damage` = `Reported_Damage`,
    `Modelled Damage Before Calibration` = `Modelled_Damage_Before_Calibration`,
    `Modelled Damage After Calibration` = `Modelled_Damage_After_Calibration`
  )
  if(nrow(storm_table) > 0) {
   kable(storm_table) %>% kable_styling(full_width = TRUE)}
}

```

## Storm Probability
```{r Storm prob, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_storm){
  # Define which benchmark to do
benchmark_name <- "STORM"

# Process your dataset
Datasets <- list()

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

if (do_plots){plotStormMap(this_benchmark, all_sim_full)}

}
```

# Summary table spatial mean
```{r Summary table, echo=FALSE, message=FALSE, warning=FALSE}
 if(nrow(summary_table) > 0) {
   kable(summary_table) %>% kable_styling(full_width = TRUE)}
```

# Model-data Agreement Metrics 
```{r Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(metric_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  metric_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", metric_table$Metric)
  #metric_table$input[["Directory"]][["New_id"]] <- as.numeric(metric_table$input[["Directory"]][["New_id"]])
  #metric_table$input[["Directory"]][["New_id"]] <- sprintf("%.3f", metric_table$input[["Directory"]][["New_id"]])
   #print the table
  kable(metric_table) %>% kable_styling(full_width = TRUE)}
```

# Forest fraction

```{r Forest fraction fraction,echo=FALSE, message=FALSE, results='hide', warning=FALSE}
if (do_forest_fraction){
  
  if (do_cmass){
benchmark_name <- "CMASS1"
  
Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

Forest_fraction_table <- bind_rows(Forest_fraction_table, DGVMBenchmarks::ForestFraction(benchmark = this_benchmark, all_Fields_list = all_Fields_list)) %>%
  dplyr::mutate(across(everything(), ~ replace_na(.x, NA)))
  }
  if (do_woody_growth){
benchmark_name <- "W_GROWTH1" 

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

Forest_fraction_table <- bind_rows(Forest_fraction_table, DGVMBenchmarks::ForestFraction(benchmark = this_benchmark, all_Fields_list = all_Fields_list)) %>%
  dplyr::mutate(across(everything(), ~ replace_na(.x, NA)))
}


if (do_cpool){
benchmark_name <- "cpool" 

Datasets <- list()

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_Fields_list[[1]]@data$tot <- all_Fields_list[[1]]@data$SoilC + all_Fields_list[[1]]@data$LitterC
all_Fields_list[[2]]@data$tot <- all_Fields_list[[2]]@data$SoilC + all_Fields_list[[2]]@data$LitterC

this_benchmark@guess_var <- "tot"

Forest_fraction_table <- bind_rows(Forest_fraction_table, DGVMBenchmarks::ForestFraction(benchmark = this_benchmark, all_Fields_list = all_Fields_list)) %>%
  dplyr::mutate(across(everything(), ~ replace_na(.x, NA)))
}
}
```

```{r forest fraction table, echo=FALSE, message=FALSE, warning=FALSE}
 if(nrow(Forest_fraction_table) > 0) {
   kable(Forest_fraction_table) %>% kable_styling(full_width = TRUE)}
```

# Fire 

# SIMFIRE difference Plots 
```{r SIMFIRE, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_SIMFIRE){
  # Define which benchmark to do
benchmark_name <- "SIMFIRE"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)

## Spatial plotting of your comparisons, handels multiple layers to.
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "difference")}



}
```

# BLAZE difference Plots 
```{r BLAZE, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_BLAZE){
  # Define which benchmark to do
benchmark_name <- "BLAZE"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)

## Spatial plotting of your comparisons, handels multiple layers to.
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "difference")}


}
```

# Profound {.tabset}

## LAI Total
```{r Profound LAI.csv, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_csv1"

Data.year.mean <- processDataSource(all_datasets = all_datasets, input, benchmark_name)

this_benchmark <- createBenchmark(benchmark_name, input, Data.year.mean, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_Fields_list[[2]]@data[, Site := paste0(tolower(Site))]
all_Fields_list[[3]]@data[, Site := paste0(tolower(Site))]

PROFOUND <- read.csv(file.path(system.file("extdata/PROFOUND/PROFOUND_Grid_List.csv", package = "DGVMBenchmarks")), header = T,sep = ",")
    setDT(PROFOUND)

all_Fields_list[[2]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

all_Fields_list[[3]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)
 
plotTemporalFields(Benchmark = this_benchmark,all_comparisons = all_comparisons, all_Fields_list = all_Fields_list, plot.option = "joined", uncertainty ="SD")

if(length(this_benchmark@datasets) != 0){Profound_table <- rbind(Profound_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## LAI Difference
```{r Profound LAI difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## CMASS Total
```{r Profound CMASS, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_cmass1"
Data.year.mean <- processDataSource(all_datasets = all_datasets, input, benchmark_name)

this_benchmark <- createBenchmark(benchmark_name, input, Data.year.mean, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_Fields_list[[2]]@data[["Forest_sum"]] <- as.numeric(all_Fields_list[[2]]@data[["Forest_sum"]])
all_Fields_list[[3]]@data[["Forest_sum"]] <- as.numeric(all_Fields_list[[3]]@data[["Forest_sum"]])
all_sim_full[[1]]@data[["Forest_sum"]] <- as.numeric(all_sim_full[[1]]@data[["Forest_sum"]])
all_sim_full[[2]]@data[["Forest_sum"]] <- as.numeric(all_sim_full[[2]]@data[["Forest_sum"]])

all_Fields_list[[2]]@data[["Forest_sum"]] <- all_Fields_list[[2]]@data[["Forest_sum"]] * 0.0001
all_Fields_list[[3]]@data[["Forest_sum"]] <- all_Fields_list[[3]]@data[["Forest_sum"]] * 0.0001

all_Fields_list[[2]]@data[, Site := paste0(tolower(Site))]
all_Fields_list[[3]]@data[, Site := paste0(tolower(Site))]

PROFOUND <- read.csv(file.path(system.file("extdata/PROFOUND/PROFOUND_Grid_List.csv", package = "DGVMBenchmarks")), header = T,sep = ",")
    setDT(PROFOUND)

all_Fields_list[[2]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

all_Fields_list[[3]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

setkey(all_Fields_list[[2]]@data)
setkey(all_Fields_list[[3]]@data)

all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)
 
plotTemporalFields(Benchmark = this_benchmark,all_comparisons = all_comparisons, all_Fields_list = all_Fields_list, plot.option = "joined", uncertainty ="SD")

if(length(this_benchmark@datasets) != 0){Profound_table <- rbind(Profound_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Cmass Difference
```{r Profound Cmass difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## DENSITY Total
```{r Profound DENS, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_dens1"

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_Fields_list[[2]]@data[, Site := paste0(tolower(Site))]
all_Fields_list[[3]]@data[, Site := paste0(tolower(Site))]

PROFOUND <- read.csv(file.path(system.file("extdata/PROFOUND/PROFOUND_Grid_List.csv", package = "DGVMBenchmarks")), header = T,sep = ",")
    setDT(PROFOUND)

all_Fields_list[[2]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

all_Fields_list[[3]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

setkey(all_Fields_list[[2]]@data)
setkey(all_Fields_list[[3]]@data)

all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)
 
plotTemporalFields(Benchmark = this_benchmark,all_comparisons = all_comparisons, all_Fields_list = all_Fields_list, plot.option = "joined", uncertainty ="SD")

if(length(this_benchmark@datasets) != 0){Profound_table <- rbind(Profound_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Density Difference
```{r Profound density difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## QDBH Total
```{r Profound QDBH, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_diam_g_plus10cm_sts_ext_st_mean1"

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_Fields_list[[2]]@data[, Site := paste0(tolower(Site))]
all_Fields_list[[3]]@data[, Site := paste0(tolower(Site))]

PROFOUND <- read.csv(file.path(system.file("extdata/PROFOUND/PROFOUND_Grid_List.csv", package = "DGVMBenchmarks")), header = T,sep = ",")
    setDT(PROFOUND)

all_Fields_list[[2]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

all_Fields_list[[3]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

setkey(all_Fields_list[[2]]@data)
setkey(all_Fields_list[[3]]@data)

all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)
 
plotTemporalFields(Benchmark = this_benchmark,all_comparisons = all_comparisons, all_Fields_list = all_Fields_list, plot.option = "joined", uncertainty ="SD")

if(length(this_benchmark@datasets) != 0){Profound_table <- rbind(Profound_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## QDBH Difference
```{r Profound QDBH difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## DBH Total
```{r Profound DBH, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){
benchmark_name <- "Profound_diam_plus10cm_sts_ext_st_mean1"
Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_Fields_list[[2]]@data[, Site := paste0(tolower(Site))]
all_Fields_list[[3]]@data[, Site := paste0(tolower(Site))]

PROFOUND <- read.csv(file.path(system.file("extdata/PROFOUND/PROFOUND_Grid_List.csv", package = "DGVMBenchmarks")), header = T,sep = ",")
    setDT(PROFOUND)

all_Fields_list[[2]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

all_Fields_list[[3]]@data[
  PROFOUND,
  c("Lat", "Lon") := .(i.Lat, i.Lon),
  on = "Site"
]

setkey(all_Fields_list[[2]]@data)
setkey(all_Fields_list[[3]]@data)

all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)
 
plotTemporalFields(Benchmark = this_benchmark,all_comparisons = all_comparisons, all_Fields_list = all_Fields_list, plot.option = "joined", uncertainty ="SD")

if(length(this_benchmark@datasets) != 0){Profound_table <- rbind(Profound_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## DBH Difference
```{r Profound DBH difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_profound){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## Profound metric table
```{r Profound Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(Profound_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  Profound_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", Profound_table$Metric)
  # Profound_table$`New Model Run` <- as.numeric(Profound_table$`New Model Run`)
  # Profound_table$`New Model Run` <- sprintf("%.3f", Profound_table$`New Model Run`)
  # Profound_table$`Old Model Run` <- as.numeric(Profound_table$`Old Model Run`)
  # Profound_table$`Old Model Run` <- sprintf("%.3f", Profound_table$`Old Model Run`)
   #print the table
  kable(Profound_table) %>% kable_styling(full_width = TRUE)}
```

# ICOS GPP{.tabset}

## Daily Total
```{r ICOS GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_GPP){
  # Define which benchmark to do
benchmark_name <- "ICOS_GPP1"

# Process your dataset
Data.year.mean <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Data.year.mean, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

## Run dataset through this function to make sure it matches with archive station info
correctICOSDataset(all_Fields_list, site.type = "Ecosystem")

##Use the correct Lat Lon from dataset to match the simulated grid format to station location
lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)

all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 51.25 & Lon == 4.75 ~ lats[[1]], # BE-Bra
      Lat == 50.25 & Lon == 4.75 ~ lats[[2]], # BE-Dor
      Lat == 50.75 & Lon == 4.75 ~ lats[[3]], # BE-Lon
      Lat == 50.75 & Lon == 5.75 ~ lats[[4]], # BE-Maa
      Lat == 50.25 & Lon == 5.75 ~ lats[[5]], # BE-Vie
      Lat == 46.75 & Lon == 9.75 ~ lats[[6]], # CH-Dav
      Lat == 49.75 & Lon == 18.75 ~ lats[[7]], # CZ-BK1
      Lat == 48.75 & Lon == 16.75 ~ lats[[8]], # CZ-Lnz
      Lat == 51.25 & Lon == 10.75 ~ lats[[9]], # DE-Geb
      Lat == 52.25 & Lon == 11.25 ~ lats[[10]], # DE-HoH
      Lat == 50.75 & Lon == 6.25 ~ lats[[11]], # DE-RuS
      Lat == 50.75 & Lon == 13.75 ~ lats[[12]], # DE-Tha
      Lat == 55.25 & Lon == 11.75 ~ lats[[13]], # DK-Sor
      Lat == 56.25 & Lon == 9.25 ~ lats[[14]], # DK-Vng
      Lat == 61.75 & Lon == 24.25 ~ lats[[15]], # FI-Hyy
      Lat == 67.25 & Lon == 26.75 ~ lats[[17]], # FI-Sod
      Lat == 44.25 & Lon == -0.75 ~ NA, # FR-Bil
      Lat == 43.25 & Lon == 5.75 ~ lats[[19]], # FR-FBn
      Lat == 48.25 & Lon == 2.75 ~ lats[[20]], # FR-Fon
      Lat == 48.75 & Lon == 1.75 ~ lats[[21]], # FR-Gri
      Lat == 48.75 & Lon == 7.25 ~ lats[[22]], # FR-Hes
      Lat == 43.25 & Lon == 1.25 ~ lats[[23]], # FR-Lam
      Lat == 45.75 & Lon == 2.75 ~ lats[[24]], # FR-Lqu
      Lat == 46.25 & Lon == 0.25 ~ lats[[25]], # FR-Lus
      Lat == 43.75 & Lon == 3.75 ~ lats[[26]], # FR-Pue
      Lat == 40.75 & Lon == 14.75 ~ lats[[28]], # IT-BCi
      Lat == 41.75 & Lon == 12.25 ~ lats[[29]], # IT-Cp2
      Lat == 46.25 & Lon == 11.25 ~ lats[[30]], # IT-MBo
      Lat == 46.75 & Lon == 11.25 ~ lats[[31]], # IT-Ren
      Lat == 43.75 & Lon == 10.25 ~ lats[[32]], # IT-SR2
      Lat == 52.25 & Lon == 5.75 ~ lats[[33]], # NL-Loo
      Lat == 56.25 & Lon == 13.25 ~ lats[[35]], # SE-Htm
      Lat == 60.25 & Lon == 17.25 ~ lats[[36]], # SE-Nor
      Lat == 68.25 & Lon == 19.25 ~ lats[[37]], # SE-Sto
      Lat == 64.25 & Lon == 19.75 ~ lats[[38]], # SE-Svb
      Lat == 55.75 & Lon == -3.25 ~ lats[[39]], # UK-AMo
      TRUE ~ Lat  # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == 4.75 & Lat == lats[[1]] ~ lons[[1]],   # BE-Bra
      Lon == 4.75 & Lat == lats[[2]] ~ lons[[2]],   # BE-Dor
      Lon == 4.75 & Lat == lats[[3]] ~ lons[[3]],   # BE-Lon
      Lon == 5.75 & Lat == lats[[4]] ~ lons[[4]],   # BE-Maa
      Lon == 5.75 & Lat == lats[[5]] ~ lons[[5]],   # BE-Vie
      Lon == 9.75 & Lat == lats[[6]] ~ lons[[6]],   # CH-Dav
      Lon == 18.75 & Lat == lats[[7]] ~ lons[[7]],  # CZ-BK1
      Lon == 16.75 & Lat == lats[[8]] ~ lons[[8]],  # CZ-Lnz
      Lon == 10.75 & Lat == lats[[9]] ~ lons[[9]],  # DE-Geb
      Lon == 11.25 & Lat == lats[[10]] ~ lons[[10]], # DE-HoH
      Lon == 6.25 & Lat == lats[[11]] ~ lons[[11]],  # DE-RuS
      Lon == 13.75 & Lat == lats[[12]] ~ lons[[12]], # DE-Tha
      Lon == 11.75 & Lat == lats[[13]] ~ lons[[13]], # DK-Sor
      Lon == 9.25 & Lat == lats[[14]] ~ lons[[14]],  # DK-Vng
      Lon == 24.25 & Lat == lats[[15]] ~ lons[[15]], # FI-Hyy
      Lon == 26.75 & Lat == lats[[17]] ~ lons[[17]], # FI-Sod
      Lon == -0.75 & Lat == NA ~ NA,         # FR-Bil
      Lon == 5.75 & Lat == lats[[19]] ~ lons[[19]],  # FR-FBn
      Lon == 2.75 & Lat == lats[[20]] ~ lons[[20]],  # FR-Fon
      Lon == 1.75 & Lat == lats[[21]] ~ lons[[21]],  # FR-Gri
      Lon == 7.25 & Lat == lats[[22]] ~ lons[[22]],  # FR-Hes
      Lon == 1.25 & Lat == lats[[23]] ~ lons[[23]],  # FR-Lam
      Lon == 2.75 & Lat == lats[[24]] ~ lons[[24]],  # FR-Lqu
      Lon == 0.25 & Lat == lats[[25]] ~ lons[[25]],  # FR-Lus
      Lon == 3.75 & Lat == lats[[26]] ~ lons[[26]],  # FR-Pue
      Lon == 14.75 & Lat == lats[[28]] ~ lons[[28]], # IT-BCi
      Lon == 12.25 & Lat == lats[[29]] ~ lons[[29]], # IT-Cp2
      Lon == 11.25 & Lat == lats[[30]] ~ lons[[30]], # IT-MBo
      Lon == 11.25 & Lat == lats[[31]] ~ lons[[31]], # IT-Ren
      Lon == 10.25 & Lat == lats[[32]] ~ lons[[32]], # IT-SR2
      Lon == 5.75 & Lat == lats[[33]] ~ lons[[33]],  # NL-Loo
      Lon == 13.25 & Lat == lats[[35]] ~ lons[[35]], # SE-Htm
      Lon == 17.25 & Lat == lats[[36]] ~ lons[[36]], # SE-Nor
      Lon == 19.25 & Lat == lats[[37]] ~ lons[[37]], # SE-Sto
      Lon == 19.75 & Lat == lats[[38]] ~ lons[[38]], # SE-Svb
      Lon == -3.25 & Lat == lats[[39]] ~ lons[[39]], # UK-AMo
      TRUE ~ Lon  # Keep the original value if none of the conditions match
    )
  )




# all_Fields_list[[3]]@data <- all_Fields_list[[3]]@data %>%
#   mutate(
#     Lat = case_when(
#       Lat == 56.25 ~ lats[[2]],
#       Lat == 60.25 ~ lats[[3]],
#       Lat == 64.25 ~ lats[[4]],
#       TRUE ~ Lat
#       # Add more conditions if needed
#         # Keep the original value if none of the conditions match
#     ),
#     Lon = case_when(
#       Lon == 13.25 ~ lons[[2]],
#       Lon == 17.25 ~ lons[[3]],
#       Lon == 19.75 ~ lons[[4]],
#       TRUE ~ Lon
#       # Add more conditions if needed
#         # Keep the original value if none of the conditions match
#     )
#   ) 

  

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)

plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## GPP Daily Difference
```{r ICOS GPP Diff, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_GPP){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## GPP per land cover
```{r ICOS GPP lu, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_GPP){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```

## GPP per Climate
```{r ICOS GPP clim, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_GPP){plotICOSScatter(this_benchmark,all_comparisons,fill="climate")}
```

## GPP per country
```{r ICOS GPP country, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_GPP){plotICOSScatter(this_benchmark,all_comparisons,fill="country")}
```

## GPP per site
```{r ICOS GPP site, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_GPP){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```


# ICOS NEE{.tabset}

## Daily Total
```{r ICOS NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_NEE){
  # Define which benchmark to do
benchmark_name <- "ICOS_NEE1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

correctICOSDataset(all_Fields_list, site.type = "Ecosystem")

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 51.25 & Lon == 4.75 ~ lats[[1]], # BE-Bra
      Lat == 50.25 & Lon == 4.75 ~ lats[[2]], # BE-Dor
      Lat == 50.75 & Lon == 4.75 ~ lats[[3]], # BE-Lon
      Lat == 50.75 & Lon == 5.75 ~ lats[[4]], # BE-Maa
      Lat == 50.25 & Lon == 5.75 ~ lats[[5]], # BE-Vie
      Lat == 46.75 & Lon == 9.75 ~ lats[[6]], # CH-Dav
      Lat == 49.75 & Lon == 18.75 ~ lats[[7]], # CZ-BK1
      Lat == 48.75 & Lon == 16.75 ~ lats[[8]], # CZ-Lnz
      Lat == 51.25 & Lon == 10.75 ~ lats[[9]], # DE-Geb
      Lat == 52.25 & Lon == 11.25 ~ lats[[10]], # DE-HoH
      Lat == 50.75 & Lon == 6.25 ~ lats[[11]], # DE-RuS
      Lat == 50.75 & Lon == 13.75 ~ lats[[12]], # DE-Tha
      Lat == 55.25 & Lon == 11.75 ~ lats[[13]], # DK-Sor
      Lat == 56.25 & Lon == 9.25 ~ lats[[14]], # DK-Vng
      Lat == 61.75 & Lon == 24.25 ~ lats[[15]], # FI-Hyy
      Lat == 67.25 & Lon == 26.75 ~ lats[[17]], # FI-Sod
      Lat == 44.25 & Lon == -0.75 ~ NA, # FR-Bil
      Lat == 43.25 & Lon == 5.75 ~ lats[[19]], # FR-FBn
      Lat == 48.25 & Lon == 2.75 ~ lats[[20]], # FR-Fon
      Lat == 48.75 & Lon == 1.75 ~ lats[[21]], # FR-Gri
      Lat == 48.75 & Lon == 7.25 ~ lats[[22]], # FR-Hes
      Lat == 43.25 & Lon == 1.25 ~ lats[[23]], # FR-Lam
      Lat == 45.75 & Lon == 2.75 ~ lats[[24]], # FR-Lqu
      Lat == 46.25 & Lon == 0.25 ~ lats[[25]], # FR-Lus
      Lat == 43.75 & Lon == 3.75 ~ lats[[26]], # FR-Pue
      Lat == 40.75 & Lon == 14.75 ~ lats[[28]], # IT-BCi
      Lat == 41.75 & Lon == 12.25 ~ lats[[29]], # IT-Cp2
      Lat == 46.25 & Lon == 11.25 ~ lats[[30]], # IT-MBo
      Lat == 46.75 & Lon == 11.25 ~ lats[[31]], # IT-Ren
      Lat == 43.75 & Lon == 10.25 ~ lats[[32]], # IT-SR2
      Lat == 52.25 & Lon == 5.75 ~ lats[[33]], # NL-Loo
      Lat == 56.25 & Lon == 13.25 ~ lats[[35]], # SE-Htm
      Lat == 60.25 & Lon == 17.25 ~ lats[[36]], # SE-Nor
      Lat == 68.25 & Lon == 19.25 ~ lats[[37]], # SE-Sto
      Lat == 64.25 & Lon == 19.75 ~ lats[[38]], # SE-Svb
      Lat == 55.75 & Lon == -3.25 ~ lats[[39]], # UK-AMo
      TRUE ~ Lat  # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == 4.75 & Lat == lats[[1]] ~ lons[[1]],   # BE-Bra
      Lon == 4.75 & Lat == lats[[2]] ~ lons[[2]],   # BE-Dor
      Lon == 4.75 & Lat == lats[[3]] ~ lons[[3]],   # BE-Lon
      Lon == 5.75 & Lat == lats[[4]] ~ lons[[4]],   # BE-Maa
      Lon == 5.75 & Lat == lats[[5]] ~ lons[[5]],   # BE-Vie
      Lon == 9.75 & Lat == lats[[6]] ~ lons[[6]],   # CH-Dav
      Lon == 18.75 & Lat == lats[[7]] ~ lons[[7]],  # CZ-BK1
      Lon == 16.75 & Lat == lats[[8]] ~ lons[[8]],  # CZ-Lnz
      Lon == 10.75 & Lat == lats[[9]] ~ lons[[9]],  # DE-Geb
      Lon == 11.25 & Lat == lats[[10]] ~ lons[[10]], # DE-HoH
      Lon == 6.25 & Lat == lats[[11]] ~ lons[[11]],  # DE-RuS
      Lon == 13.75 & Lat == lats[[12]] ~ lons[[12]], # DE-Tha
      Lon == 11.75 & Lat == lats[[13]] ~ lons[[13]], # DK-Sor
      Lon == 9.25 & Lat == lats[[14]] ~ lons[[14]],  # DK-Vng
      Lon == 24.25 & Lat == lats[[15]] ~ lons[[15]], # FI-Hyy
      Lon == 26.75 & Lat == lats[[17]] ~ lons[[17]], # FI-Sod
      Lon == -0.75 & Lat == NA ~ NA,         # FR-Bil
      Lon == 5.75 & Lat == lats[[19]] ~ lons[[19]],  # FR-FBn
      Lon == 2.75 & Lat == lats[[20]] ~ lons[[20]],  # FR-Fon
      Lon == 1.75 & Lat == lats[[21]] ~ lons[[21]],  # FR-Gri
      Lon == 7.25 & Lat == lats[[22]] ~ lons[[22]],  # FR-Hes
      Lon == 1.25 & Lat == lats[[23]] ~ lons[[23]],  # FR-Lam
      Lon == 2.75 & Lat == lats[[24]] ~ lons[[24]],  # FR-Lqu
      Lon == 0.25 & Lat == lats[[25]] ~ lons[[25]],  # FR-Lus
      Lon == 3.75 & Lat == lats[[26]] ~ lons[[26]],  # FR-Pue
      Lon == 14.75 & Lat == lats[[28]] ~ lons[[28]], # IT-BCi
      Lon == 12.25 & Lat == lats[[29]] ~ lons[[29]], # IT-Cp2
      Lon == 11.25 & Lat == lats[[30]] ~ lons[[30]], # IT-MBo
      Lon == 11.25 & Lat == lats[[31]] ~ lons[[31]], # IT-Ren
      Lon == 10.25 & Lat == lats[[32]] ~ lons[[32]], # IT-SR2
      Lon == 5.75 & Lat == lats[[33]] ~ lons[[33]],  # NL-Loo
      Lon == 13.25 & Lat == lats[[35]] ~ lons[[35]], # SE-Htm
      Lon == 17.25 & Lat == lats[[36]] ~ lons[[36]], # SE-Nor
      Lon == 19.25 & Lat == lats[[37]] ~ lons[[37]], # SE-Sto
      Lon == 19.75 & Lat == lats[[38]] ~ lons[[38]], # SE-Svb
      Lon == -3.25 & Lat == lats[[39]] ~ lons[[39]], # UK-AMo
      TRUE ~ Lon  # Keep the original value if none of the conditions match
    )
  )
  
## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)

plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## NEE Daily Difference
```{r ICOS NEE Diff, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_NEE){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## NEE per land cover
```{r ICOS NEE lu, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_NEE){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```

## NEE per Climate
```{r ICOS NEE clim, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_NEE){plotICOSScatter(this_benchmark,all_comparisons,fill="climate")}
```

## NEE per country
```{r ICOS NEE country, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_NEE){plotICOSScatter(this_benchmark,all_comparisons,fill="country")}
```

## NEE per site
```{r ICOS NEE site, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_NEE){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```

# ICOS Reco{.tabset}

## Daily Total
```{r ICOS Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_Reco){
  # Define which benchmark to do
benchmark_name <- "ICOS_Reco1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

correctICOSDataset(all_Fields_list, site.type = "Ecosystem")

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 51.25 & Lon == 4.75 ~ lats[[1]], # BE-Bra
      Lat == 50.25 & Lon == 4.75 ~ lats[[2]], # BE-Dor
      Lat == 50.75 & Lon == 4.75 ~ lats[[3]], # BE-Lon
      Lat == 50.75 & Lon == 5.75 ~ lats[[4]], # BE-Maa
      Lat == 50.25 & Lon == 5.75 ~ lats[[5]], # BE-Vie
      Lat == 46.75 & Lon == 9.75 ~ lats[[6]], # CH-Dav
      Lat == 49.75 & Lon == 18.75 ~ lats[[7]], # CZ-BK1
      Lat == 48.75 & Lon == 16.75 ~ lats[[8]], # CZ-Lnz
      Lat == 51.25 & Lon == 10.75 ~ lats[[9]], # DE-Geb
      Lat == 52.25 & Lon == 11.25 ~ lats[[10]], # DE-HoH
      Lat == 50.75 & Lon == 6.25 ~ lats[[11]], # DE-RuS
      Lat == 50.75 & Lon == 13.75 ~ lats[[12]], # DE-Tha
      Lat == 55.25 & Lon == 11.75 ~ lats[[13]], # DK-Sor
      Lat == 56.25 & Lon == 9.25 ~ lats[[14]], # DK-Vng
      Lat == 61.75 & Lon == 24.25 ~ lats[[15]], # FI-Hyy
      Lat == 67.25 & Lon == 26.75 ~ lats[[17]], # FI-Sod
      Lat == 44.25 & Lon == -0.75 ~ NA, # FR-Bil
      Lat == 43.25 & Lon == 5.75 ~ lats[[19]], # FR-FBn
      Lat == 48.25 & Lon == 2.75 ~ lats[[20]], # FR-Fon
      Lat == 48.75 & Lon == 1.75 ~ lats[[21]], # FR-Gri
      Lat == 48.75 & Lon == 7.25 ~ lats[[22]], # FR-Hes
      Lat == 43.25 & Lon == 1.25 ~ lats[[23]], # FR-Lam
      Lat == 45.75 & Lon == 2.75 ~ lats[[24]], # FR-Lqu
      Lat == 46.25 & Lon == 0.25 ~ lats[[25]], # FR-Lus
      Lat == 43.75 & Lon == 3.75 ~ lats[[26]], # FR-Pue
      Lat == 40.75 & Lon == 14.75 ~ lats[[28]], # IT-BCi
      Lat == 41.75 & Lon == 12.25 ~ lats[[29]], # IT-Cp2
      Lat == 46.25 & Lon == 11.25 ~ lats[[30]], # IT-MBo
      Lat == 46.75 & Lon == 11.25 ~ lats[[31]], # IT-Ren
      Lat == 43.75 & Lon == 10.25 ~ lats[[32]], # IT-SR2
      Lat == 52.25 & Lon == 5.75 ~ lats[[33]], # NL-Loo
      Lat == 56.25 & Lon == 13.25 ~ lats[[35]], # SE-Htm
      Lat == 60.25 & Lon == 17.25 ~ lats[[36]], # SE-Nor
      Lat == 68.25 & Lon == 19.25 ~ lats[[37]], # SE-Sto
      Lat == 64.25 & Lon == 19.75 ~ lats[[38]], # SE-Svb
      Lat == 55.75 & Lon == -3.25 ~ lats[[39]], # UK-AMo
      TRUE ~ Lat  # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == 4.75 & Lat == lats[[1]] ~ lons[[1]],   # BE-Bra
      Lon == 4.75 & Lat == lats[[2]] ~ lons[[2]],   # BE-Dor
      Lon == 4.75 & Lat == lats[[3]] ~ lons[[3]],   # BE-Lon
      Lon == 5.75 & Lat == lats[[4]] ~ lons[[4]],   # BE-Maa
      Lon == 5.75 & Lat == lats[[5]] ~ lons[[5]],   # BE-Vie
      Lon == 9.75 & Lat == lats[[6]] ~ lons[[6]],   # CH-Dav
      Lon == 18.75 & Lat == lats[[7]] ~ lons[[7]],  # CZ-BK1
      Lon == 16.75 & Lat == lats[[8]] ~ lons[[8]],  # CZ-Lnz
      Lon == 10.75 & Lat == lats[[9]] ~ lons[[9]],  # DE-Geb
      Lon == 11.25 & Lat == lats[[10]] ~ lons[[10]], # DE-HoH
      Lon == 6.25 & Lat == lats[[11]] ~ lons[[11]],  # DE-RuS
      Lon == 13.75 & Lat == lats[[12]] ~ lons[[12]], # DE-Tha
      Lon == 11.75 & Lat == lats[[13]] ~ lons[[13]], # DK-Sor
      Lon == 9.25 & Lat == lats[[14]] ~ lons[[14]],  # DK-Vng
      Lon == 24.25 & Lat == lats[[15]] ~ lons[[15]], # FI-Hyy
      Lon == 26.75 & Lat == lats[[17]] ~ lons[[17]], # FI-Sod
      Lon == -0.75 & Lat == NA ~ NA,         # FR-Bil
      Lon == 5.75 & Lat == lats[[19]] ~ lons[[19]],  # FR-FBn
      Lon == 2.75 & Lat == lats[[20]] ~ lons[[20]],  # FR-Fon
      Lon == 1.75 & Lat == lats[[21]] ~ lons[[21]],  # FR-Gri
      Lon == 7.25 & Lat == lats[[22]] ~ lons[[22]],  # FR-Hes
      Lon == 1.25 & Lat == lats[[23]] ~ lons[[23]],  # FR-Lam
      Lon == 2.75 & Lat == lats[[24]] ~ lons[[24]],  # FR-Lqu
      Lon == 0.25 & Lat == lats[[25]] ~ lons[[25]],  # FR-Lus
      Lon == 3.75 & Lat == lats[[26]] ~ lons[[26]],  # FR-Pue
      Lon == 14.75 & Lat == lats[[28]] ~ lons[[28]], # IT-BCi
      Lon == 12.25 & Lat == lats[[29]] ~ lons[[29]], # IT-Cp2
      Lon == 11.25 & Lat == lats[[30]] ~ lons[[30]], # IT-MBo
      Lon == 11.25 & Lat == lats[[31]] ~ lons[[31]], # IT-Ren
      Lon == 10.25 & Lat == lats[[32]] ~ lons[[32]], # IT-SR2
      Lon == 5.75 & Lat == lats[[33]] ~ lons[[33]],  # NL-Loo
      Lon == 13.25 & Lat == lats[[35]] ~ lons[[35]], # SE-Htm
      Lon == 17.25 & Lat == lats[[36]] ~ lons[[36]], # SE-Nor
      Lon == 19.25 & Lat == lats[[37]] ~ lons[[37]], # SE-Sto
      Lon == 19.75 & Lat == lats[[38]] ~ lons[[38]], # SE-Svb
      Lon == -3.25 & Lat == lats[[39]] ~ lons[[39]], # UK-AMo
      TRUE ~ Lon  # Keep the original value if none of the conditions match
    )
  )
  
## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)

plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Reco Daily Difference
```{r ICOS Reco Diff, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_Reco){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## Reco per land cover
```{r ICOS Reco lu, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_Reco){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```

## Reco per Climate
```{r ICOS Reco clim, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_Reco){plotICOSScatter(this_benchmark,all_comparisons,fill="climate")}
```

## Reco per country
```{r ICOS Reco country, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_Reco){plotICOSScatter(this_benchmark,all_comparisons,fill="country")}
```

## Reco per site
```{r ICOS Reco site, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_Reco){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```

# ICOS Evapotranspiration{.tabset}

## Daily Total
```{r ICOS ET, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_ET){
  # Define which benchmark to do
benchmark_name <- "ICOS_ET1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Convert Latent heat flux to Evapotranspiration from W/m^2 -> mm/day
latent_heat_of_vaporization <- 2.45

Datasets[["ICOS"]]@data$ET <- (Datasets[["ICOS"]]@data$LE * 86400) / (latent_heat_of_vaporization * 1e6)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

correctICOSDataset(all_Fields_list, site.type = "Ecosystem")

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 51.25 & Lon == 4.75 ~ lats[[1]], # BE-Bra
      Lat == 50.25 & Lon == 4.75 ~ lats[[2]], # BE-Dor
      Lat == 50.75 & Lon == 4.75 ~ lats[[3]], # BE-Lon
      Lat == 50.75 & Lon == 5.75 ~ lats[[4]], # BE-Maa
      Lat == 50.25 & Lon == 5.75 ~ lats[[5]], # BE-Vie
      Lat == 46.75 & Lon == 9.75 ~ lats[[6]], # CH-Dav
      Lat == 49.75 & Lon == 18.75 ~ lats[[7]], # CZ-BK1
      Lat == 48.75 & Lon == 16.75 ~ lats[[8]], # CZ-Lnz
      Lat == 51.25 & Lon == 10.75 ~ lats[[9]], # DE-Geb
      Lat == 52.25 & Lon == 11.25 ~ lats[[10]], # DE-HoH
      Lat == 50.75 & Lon == 6.25 ~ lats[[11]], # DE-RuS
      Lat == 50.75 & Lon == 13.75 ~ lats[[12]], # DE-Tha
      Lat == 55.25 & Lon == 11.75 ~ lats[[13]], # DK-Sor
      Lat == 56.25 & Lon == 9.25 ~ lats[[14]], # DK-Vng
      Lat == 61.75 & Lon == 24.25 ~ lats[[15]], # FI-Hyy
      Lat == 67.25 & Lon == 26.75 ~ lats[[17]], # FI-Sod
      Lat == 44.25 & Lon == -0.75 ~ NA, # FR-Bil
      Lat == 43.25 & Lon == 5.75 ~ lats[[19]], # FR-FBn
      Lat == 48.25 & Lon == 2.75 ~ lats[[20]], # FR-Fon
      Lat == 48.75 & Lon == 1.75 ~ lats[[21]], # FR-Gri
      Lat == 48.75 & Lon == 7.25 ~ lats[[22]], # FR-Hes
      Lat == 43.25 & Lon == 1.25 ~ lats[[23]], # FR-Lam
      Lat == 45.75 & Lon == 2.75 ~ lats[[24]], # FR-Lqu
      Lat == 46.25 & Lon == 0.25 ~ lats[[25]], # FR-Lus
      Lat == 43.75 & Lon == 3.75 ~ lats[[26]], # FR-Pue
      Lat == 40.75 & Lon == 14.75 ~ lats[[28]], # IT-BCi
      Lat == 41.75 & Lon == 12.25 ~ lats[[29]], # IT-Cp2
      Lat == 46.25 & Lon == 11.25 ~ lats[[30]], # IT-MBo
      Lat == 46.75 & Lon == 11.25 ~ lats[[31]], # IT-Ren
      Lat == 43.75 & Lon == 10.25 ~ lats[[32]], # IT-SR2
      Lat == 52.25 & Lon == 5.75 ~ lats[[33]], # NL-Loo
      Lat == 56.25 & Lon == 13.25 ~ lats[[35]], # SE-Htm
      Lat == 60.25 & Lon == 17.25 ~ lats[[36]], # SE-Nor
      Lat == 68.25 & Lon == 19.25 ~ lats[[37]], # SE-Sto
      Lat == 64.25 & Lon == 19.75 ~ lats[[38]], # SE-Svb
      Lat == 55.75 & Lon == -3.25 ~ lats[[39]], # UK-AMo
      TRUE ~ Lat  # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == 4.75 & Lat == lats[[1]] ~ lons[[1]],   # BE-Bra
      Lon == 4.75 & Lat == lats[[2]] ~ lons[[2]],   # BE-Dor
      Lon == 4.75 & Lat == lats[[3]] ~ lons[[3]],   # BE-Lon
      Lon == 5.75 & Lat == lats[[4]] ~ lons[[4]],   # BE-Maa
      Lon == 5.75 & Lat == lats[[5]] ~ lons[[5]],   # BE-Vie
      Lon == 9.75 & Lat == lats[[6]] ~ lons[[6]],   # CH-Dav
      Lon == 18.75 & Lat == lats[[7]] ~ lons[[7]],  # CZ-BK1
      Lon == 16.75 & Lat == lats[[8]] ~ lons[[8]],  # CZ-Lnz
      Lon == 10.75 & Lat == lats[[9]] ~ lons[[9]],  # DE-Geb
      Lon == 11.25 & Lat == lats[[10]] ~ lons[[10]], # DE-HoH
      Lon == 6.25 & Lat == lats[[11]] ~ lons[[11]],  # DE-RuS
      Lon == 13.75 & Lat == lats[[12]] ~ lons[[12]], # DE-Tha
      Lon == 11.75 & Lat == lats[[13]] ~ lons[[13]], # DK-Sor
      Lon == 9.25 & Lat == lats[[14]] ~ lons[[14]],  # DK-Vng
      Lon == 24.25 & Lat == lats[[15]] ~ lons[[15]], # FI-Hyy
      Lon == 26.75 & Lat == lats[[17]] ~ lons[[17]], # FI-Sod
      Lon == -0.75 & Lat == NA ~ NA,         # FR-Bil
      Lon == 5.75 & Lat == lats[[19]] ~ lons[[19]],  # FR-FBn
      Lon == 2.75 & Lat == lats[[20]] ~ lons[[20]],  # FR-Fon
      Lon == 1.75 & Lat == lats[[21]] ~ lons[[21]],  # FR-Gri
      Lon == 7.25 & Lat == lats[[22]] ~ lons[[22]],  # FR-Hes
      Lon == 1.25 & Lat == lats[[23]] ~ lons[[23]],  # FR-Lam
      Lon == 2.75 & Lat == lats[[24]] ~ lons[[24]],  # FR-Lqu
      Lon == 0.25 & Lat == lats[[25]] ~ lons[[25]],  # FR-Lus
      Lon == 3.75 & Lat == lats[[26]] ~ lons[[26]],  # FR-Pue
      Lon == 14.75 & Lat == lats[[28]] ~ lons[[28]], # IT-BCi
      Lon == 12.25 & Lat == lats[[29]] ~ lons[[29]], # IT-Cp2
      Lon == 11.25 & Lat == lats[[30]] ~ lons[[30]], # IT-MBo
      Lon == 11.25 & Lat == lats[[31]] ~ lons[[31]], # IT-Ren
      Lon == 10.25 & Lat == lats[[32]] ~ lons[[32]], # IT-SR2
      Lon == 5.75 & Lat == lats[[33]] ~ lons[[33]],  # NL-Loo
      Lon == 13.25 & Lat == lats[[35]] ~ lons[[35]], # SE-Htm
      Lon == 17.25 & Lat == lats[[36]] ~ lons[[36]], # SE-Nor
      Lon == 19.25 & Lat == lats[[37]] ~ lons[[37]], # SE-Sto
      Lon == 19.75 & Lat == lats[[38]] ~ lons[[38]], # SE-Svb
      Lon == -3.25 & Lat == lats[[39]] ~ lons[[39]], # UK-AMo
      TRUE ~ Lon  # Keep the original value if none of the conditions match
    )
  )


  all_Fields_list[[1]]@data$GPP <- all_Fields_list[[1]]@data$GPP/2
  all_Fields_list[[2]]@data$GPP <- all_Fields_list[[2]]@data$GPP/2
  
## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)

plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## ET Daily Difference
```{r ICOS ET Diff, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_ET){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## ET per land cover
```{r ICOS ET lu, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_ET){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```

## ET per Climate
```{r ICOS ET clim, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_ET){plotICOSScatter(this_benchmark,all_comparisons,fill="climate")}
```

## ET per country
```{r ICOS ET country, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_ET){plotICOSScatter(this_benchmark,all_comparisons,fill="country")}
```

## ET per site
```{r ICOS ET site, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_ICOS_ET){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```


# ICOS metric table
```{r ICOS Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(ICOS_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  ICOS_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", ICOS_table$Metric)
  # Profound_table$`New Model Run` <- as.numeric(Profound_table$`New Model Run`)
  # Profound_table$`New Model Run` <- sprintf("%.3f", Profound_table$`New Model Run`)
  # Profound_table$`Old Model Run` <- as.numeric(Profound_table$`Old Model Run`)
  # Profound_table$`Old Model Run` <- sprintf("%.3f", Profound_table$`Old Model Run`)
   #print the table
  kable(ICOS_table) %>% kable_styling(full_width = TRUE)}
```

# FLUXNET bias corrected GPP {.tabset}

## Daily Total
```{r FLUXNET GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_GPP1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
this_benchmark@datasets[[1]]@spatial.extent$Lon <- lons
this_benchmark@datasets[[1]]@spatial.extent$Lat <- lats

all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

all_Fields_list[[3]]@data <- all_Fields_list[[3]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Daily Difference
```{r Difference Flux GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## GPP per site
```{r per site flux GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## GPP per Land cover
```{r per lc flux GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```


# FLUXNET bias corrected NEE {.tabset}


## Daily Total
```{r FLUXNET NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_NEE1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)
# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
this_benchmark@datasets[[1]]@spatial.extent$Lon <- lons
this_benchmark@datasets[[1]]@spatial.extent$Lat <- lats

all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

all_Fields_list[[3]]@data <- all_Fields_list[[3]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```


## NEE Daily Difference
```{r Difference Flux NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## NEE per site
```{r per site flux NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## NEE per Land cover
```{r per lc flux NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```

# FLUXNET bias corrected Reco {.tabset}

## Daily Total
```{r FLUXNET Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_Reco1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)
# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
this_benchmark@datasets[[1]]@spatial.extent$Lon <- lons
this_benchmark@datasets[[1]]@spatial.extent$Lat <- lats

all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

all_Fields_list[[3]]@data <- all_Fields_list[[3]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```


## Reco Daily Difference
```{r Difference Flux Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## Reco per site
```{r per site flux Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## Reco per Land cover
```{r per lc flux Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```


# FLUXNET CRUJRA_v2.4.5d GPP {.tabset}

## Daily Total
```{r FLUXNET GPP crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_GPP1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)
# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
this_benchmark@datasets[[1]]@spatial.extent$Lon <- lons
this_benchmark@datasets[[1]]@spatial.extent$Lat <- lats

all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

all_Fields_list[[3]]@data <- all_Fields_list[[3]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Daily Difference
```{r Difference Flux GPP crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## GPP per site
```{r per site flux GPP crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## GPP per Land cover
```{r per lc flux GPP crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_GPP){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```

# FLUXNET CRUJRA_v2.4.5d NEE {.tabset}

## Daily Total
```{r FLUXNET NEE crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_NEE1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)
# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
this_benchmark@datasets[[1]]@spatial.extent$Lon <- lons
this_benchmark@datasets[[1]]@spatial.extent$Lat <- lats

all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

all_Fields_list[[3]]@data <- all_Fields_list[[3]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## NEE Daily Difference
```{r Difference Flux NEE crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## NEE per site
```{r per site flux NEE crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## NEE per Land cover
```{r per lc flux NEE crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_NEE){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```

# FLUXNET CRUJRA_v2.4.5d Reco {.tabset}

## Daily Total
```{r FLUXNET Reco crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_Reco1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)
# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

lats <- unique(all_Fields_list[[1]]@data$Lat)
lons <- unique(all_Fields_list[[1]]@data$Lon)
this_benchmark@datasets[[1]]@spatial.extent$Lon <- lons
this_benchmark@datasets[[1]]@spatial.extent$Lat <- lats

all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

all_Fields_list[[3]]@data <- all_Fields_list[[3]]@data %>%
  mutate(
    Lat = case_when(
      Lat == 36.75 ~ lats[[1]],
      Lat == 44.75 ~ lats[[2]],
      Lat == 48.75 ~ lats[[3]],
      Lat == 50.75 ~ lats[[4]],
      Lat == 52.25 ~ lats[[5]],
      Lat == 47.25 ~ lats[[6]],
      Lat == 51.25 ~ lats[[7]],
      TRUE ~ Lat
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    ),
    Lon = case_when(
      Lon == -2.75 ~ lons[[1]],
      Lon == -0.75 ~ lons[[2]],
      Lon == 1.75 ~ lons[[3]],
      Lon == 4.75 ~ lons[[4]],
      Lon == 5.25 ~ lons[[5]],
      Lon == 8.25 ~ lons[[6]],
      Lon == 10.25 ~ lons[[7]],
      TRUE ~ Lon
      # Add more conditions if needed
        # Keep the original value if none of the conditions match
    )
  ) 

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Reco Daily Difference
```{r Difference Flux Reco crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## Reco per site
```{r per site flux Reco crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## Reco per Land cover
```{r per lc flux Reco crujra, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_FLUXNET_Reco){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```

# FLUXNET metric table
```{r FLUXNET Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(FLUXNET_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  FLUXNET_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", FLUXNET_table$Metric)
  # Profound_table$`New Model Run` <- as.numeric(Profound_table$`New Model Run`)
  # Profound_table$`New Model Run` <- sprintf("%.3f", Profound_table$`New Model Run`)
  # Profound_table$`Old Model Run` <- as.numeric(Profound_table$`Old Model Run`)
  # Profound_table$`Old Model Run` <- sprintf("%.3f", Profound_table$`Old Model Run`)
   #print the table
  kable(FLUXNET_table) %>% kable_styling(full_width = TRUE)}
```

# Timing
Total run time:
``` {r time,echo=FALSE,message=FALSE}
# report total run time
toc()
```
